Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analyst | AI&nbsp;&&nbsp;DH&nbsp;instructor </font>

### 2023-10-03 index.Rmd
aff

### What I do  
<div style="text-align: justify; padding-left:1px"> 
I work on **language and culture dynamics**, using large corpora, machine learning & AI, and cognitive experiments. Recently I have been also working on, through various collaborations, on art history and creative industries, and advising collaborative projects between academia and the public and private sectors. I am affiliated as a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, and at the [Estonian Business School](https://www.ebs.ee/en). <br>
I did my PhD at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of the University of Edinburgh, on lexical dynamics and communicative need in language. <br>
I also occasionally do workshops on **R**, stats & data visualization and **AI**-related things (see [more here](https://datafigure.eu)).

@@

Research fellow, CUDAN Open Lab, Tallinn University <br>
Instructor at Datafigure OÜ

Email: andres.karjus --at-- tlu.ee <br>
Twitter: <a href="https://twitter.com/AndresKarjus">https://twitter.com/AndresKarjus</a> <br>
Mastodon: <a href=https://mastodon.social/@andreskarjus>https://mastodon.social/@AndresKarjus</a>
<br>
LinkedIn: <a href="https://www.linkedin.com/in/andreskarjus/">https://www.linkedin.com/in/andreskarjus/</a> <br> 
</div>

>>>>

### What I do  
<div style="text-align: justify; padding-left:1px"> 
I work on **language and culture dynamics**, using large corpora, machine learning & AI, and cognitive experiments. Recently I have been also working on, through various collaborations, on art history and creative industries, and advising collaborative projects between academia and the public and private sectors. I am affiliated as a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, and at the [Estonian Business School](https://www.ebs.ee/en).
I did my PhD at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of the University of Edinburgh, on lexical dynamics and communicative need in language. <br>
I also occasionally do workshops on **R**, stats & data visualization, and **AI**-related things (see [more here](https://datafigure.eu)).

@@

Research fellow at <a href=https://cudan.tlu.ee>CUDAN Open Lab, Tallinn University</a> <br>
Senior research fellow at <a href=https://www.ebs.ee>Estonian Business School</a> <br>
Instructor at <a href=https://datafigure.eu>Datafigure OÜ</a>

Academic email: andres.karjus --at-- tlu.ee <br>
Business/workshop inquiries: please contact via the Datafigure page 
<br>
<br>
Twitter / X: <a href=https://twitter.com/AndresKarjus>twitter.com/AndresKarjus</a> <br>
Bluesky: <a href=https://bsky.app/profile/andreskarjus.bsky.social>andreskarjus.bsky.social</a> <br>
Mastodon: <a href=https://mastodon.social/@andreskarjus>mastodon.social/@AndresKarjus</a>
<br>
LinkedIn: <a href="https://www.linkedin.com/in/andreskarjus/">www.linkedin.com/in/andreskarjus/</a> <br> 
</div>
